Accessible, realistic genome simulation with selection using \stdpopsim

### 2025-07-22 analysis2_manuscript.tex
Update analysis2_manuscript.tex

    A second important finding is that inference of the DFE
    is sensitive to the dominance of deleterious mutations.
    All three of the DFE-inference methods applied here assume that deleterious mutations act
    in an additive fashion ($h=0.5$) by default.
    However, the simulated DFE for the vaquita genome included highly recessive mutations.
    Specifically, these simulations used a DFE where mutations with $s<-0.01$ are quite recessive,
    with $h<=0.01$, and where mutations with $-0.01<s<-0.001$ have $h=0.1$.
    We found that the three DFE-inference methods underestimated $E[s]$ and overestimated the shape parameter (Figure \ref{fig:vaquita-dfe}A-B).
    This performance is not surprising since decreasing $h$ for a given distribution of $s$ will lead to a decrease in $hs$,
    or an apparent decrease in the amount of selection.
    Thus, fitting a mis-specified DFE that assumes $h=0.5$ leads to underestimates of $E[s]$. \revpoint{1}{7}
    %IG: added this to respond to comment 1.7.
    %IG: I quote this in the response, so if we edit this, we should copy modified version to the response.
    Our analysis suggests that the distributions of $s$ estimated by these methods
    provide a reasonable approximation for the true distribution of $hs$ (Figure \ref{fig:vaquita-dfe}C).
    This points to a notable limitation of most existing DFE inference methods,
    which assume that selection coefficients are gamma-distributed.
    %DRS: Is the limitatio here that selection coefficients are gamma-distributed, or rather that h is fixed?
    As shown in Figure \ref{fig:vaquita-dfe}C,
    while a gamma distribution might fit the distribution of $s$, a relationship between $h$ and $s$ might result in
    $hs$ which is not well approximated by a gamma distribution.

>>>>

    A second important finding is that inference of the DFE
    is sensitive to the dominance of deleterious mutations.
    All three of the DFE-inference methods applied here assume that deleterious mutations act
    in an additive fashion ($h=0.5$) by default.
    However, the simulated DFE for the vaquita genome included highly recessive mutations.
    Specifically, these simulations used a DFE where mutations with $s<-0.01$ are quite recessive,
    with $h<=0.01$, and where mutations with $-0.01<s<-0.001$ have $h=0.1$.
    We found that the three DFE-inference methods underestimated $E[s]$ and overestimated the shape parameter (Figure \ref{fig:vaquita-dfe}A-B).
    This performance is not surprising since decreasing $h$ for a given distribution of $s$ will lead to a decrease in $hs$,
    or an apparent decrease in the amount of selection.
    Thus, fitting a mis-specified DFE that assumes $h=0.5$ leads to underestimates of $E[s]$. \revpoint{1}{7}
    %IG: added this to respond to comment 1.7.
    %IG: I quote this in the response, so if we edit this, we should copy modified version to the response.
    Our analysis suggests that the distributions of $s$ estimated by these methods
    provide a reasonable approximation for the true distribution of $hs$ (Figure \ref{fig:vaquita-dfe}C).
    This points to a notable limitation of most existing DFE inference methods,
    which assume that selection coefficients are gamma-distributed.
    %DRS: Is the limitatio here that selection coefficients are gamma-distributed, or rather that h is fixed?
    As shown in Figure \ref{fig:vaquita-dfe}C,
    while a gamma distribution might fit the conditional distribution of $s$ given $h$, a relationship between $h$ and $s$ might result in a magrinal distribution for $hs$ which is not well approximated by a gamma distribution.
